Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip

### 2014-09-08 trunk/PAPER/paper.tex
fixes for review
quasi-final submission

% Elsevier specific styles
%------------------------------------------------------------------------------
\documentclass[preprint]{elsarticle}
%\documentclass[3p]{elsarticle}
\usepackage{lineno,hyperref}

@@

\journal{Journal of \LaTeX\ Templates}

@@

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\disr}{{\sf DiSR}}
%\renewcommand{\baselinestretch}{0.97}\normalsize
%------------------------------------------------------------------------------

@@

\title{Distributed Topology Discovery in Self-Assembled Nano Networks}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

@@

%\bibliographystyle{elsarticle-num}
\section*{References}
\bibliography{bibliography}
%------------------------------------------------------------------------------

>>>>

% Elsevier specific styles
%------------------------------------------------------------------------------
\documentclass[preprint]{elsarticle}
\usepackage{lineno,hyperref}

@@

\journal{Computers \& Electrical Engineering}

@@

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\disr}{{\sf DiSR}}
%\renewcommand{\baselinestretch}{0.97}\normalsize
%------------------------------------------------------------------------------
\usepackage{color,soul}
%------------------------------------------------------------------------------

@@

\title{Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip}

%% Group authors per affiliation:
\author{Vincenzo Catania}
\ead{vincenzo.catania@dieei.unict.it}
\author{Andrea Mineo}
\ead{andrea.mineo@dieei.unict.it}
\author{Salvatore Monteleone}
\ead{salvatore.monteleone@dieei.unict.it}
\author{Davide Patti\corref{corr1}}
\ead{davide.patti@dieei.unict.it}
\address{DIEEI, University of Catania, v.le Andrea Doria 6, 95125 Catania, Italy}

\cortext[corr1]{Corresponding author}

@@

%\bibliographystyle{elsarticle-num}
\section*{References}
\bibliography{bibliography}
%------------------------------------------------------------------------------
\vspace{10 mm}

Vincenzo Catania received the Laurea degree in electrical engineering
from the University of Catania, Italy, in 1982. Until 1984, he was
responsible for testing microprocessor system at STMicroelectronics,
Catania. He is a full professor of computer
science. His research interests include performance and reliability
assessment in parallel and distributed system, VLSI design, low power
design, and fuzzy logic.

Andrea Mineo received the B.Sc. and M.Sc. degrees in Electronic
Engineering from the University of Catania, Italy, in 2010 and 2013,
respectively, and is currently pursuing the Ph.D. degree in Systems,
Energy, Computer and Telecommunications Engineering at the University
of Catania.  His current research interests are VLSI systems,
network-on-chip architectures  and emerging interconnect technologies
for on-chip networks.

Salvatore Monteleone is a post-doctoral research assistant at the
Department of Electrical, Electronic and Computer Engineering -
University of Catania, Italy. He obtained the BSc (2007) and MSc
(2010) in Computer Engineering at University of Catania where he also
completed the PhD course in Communications and Computer Engineering
(2014).  His interests comprehend cooperative systems, user-centric
systems and NoC.

Davide Patti received the Laurea and PhD degrees in computer
engineering from the University of Catania, Italy, in 2003 and 2007,
respectively. His research focuses on Design Space exploration of VLIW
systems, Network-on-Chip architectures, DNA self-assembled networks
and Human-computer interface. He is currently research assistant
at University of Catania.
